%-------------------------
% Resume in Latex
% Author : Rohith Muthukumar
% Template from: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Rohith Muthukumar}} & Email : \href{mailto:m.hari.rohith1@gmail.com}{m.hari.rohith1@gmail.com}\\
   & Mobile : +1-669-246-0506 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Monta Vista High School}{Cupertino, CA}
      {High School Diploma; GPA: 3.86 (UW)}{Aug. 2020 -- present}
      \resumeItemListStart
        \resumeItem{Expected Graduation}
            {June 2024}
        \resumeItem{Advanced Coursework}
            {AP Calculus BC (5), AP Physics C: Mechanics (5), AP Physics C: Electricity \& Magnetism (4), AP Chemistry, AP Physics 1 (5), AP Computer Science A (5), AP Government \& Politics, AP Macroeconomics, Honors American Literature, Precalculus Honors}
        \resumeItem{Self-study courses}
            {AP English Language and Composition (3)}
        \resumeItem{Activities \& Societies}
            {Monta Vista Robotics Team, Monta Vista Badminton Team, Game Development Club, Student Tutor (Calculus BC)}
        \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Monta Vista Robotics Team}{Cupertino, CA}
      {Lead Software Developer, Super Scout}{Sep 2020 - Present}
      \resumeItemListStart
        \resumeItem{Java \& WPILib}
          {Used WPILib to create robotics systems. Led the development of Climber and Elevator subsystems. Worked with mechanical components like motors, servos and ratchets. Integrated Command-Subsystem architecture to create smooth motion. Used techniques like Proportional Integral Derivative (PID) control, Trapezoidal Motion Profiling, Feed Forward control and Motion Magic to create smooth motion systems. Applied concepts in physics like voltage, gear-ratios and torque to write efficient code. Learned tools for analyzing motion profiles like AdvantageScope.}
        \resumeItem{React \& React Native}
          {Developed front end, mobile application using React Native for members to input data regarding performance of other teams during tournaments. Transformed already existing web application to provide graphical user interface and create an interface to easily analyze data gathered from competitions. Organized meetings with other members. Created dedicated timelines to meet goals. Streamlined data collection processes by creating organizing data format.}
        \resumeItem{Firebase}
            {Created and maintained accurate records of data in Firebase. Integrated applications with database. Developed programmatic methods of ensuring data safety and correct format.}
        \resumeItem{Super Scout}
            {Led team of members to collect data regarding the performance of other robots during competitions. Collaboratively analyzed data to decide and select partners for playoff rounds.}
      \resumeItemListEnd

    \resumeSubheading
      {California Tamil Academy}{Cupertino, CA}
      {Teaching Assistant}{Aug 2020 - present}
      \resumeItemListStart
        \resumeItem{Teaching assistant}
          {Assisted teachers in managing students under 7 years old. Graded home works and maintained a healthy classroom environment. Involved all students by participating in cultural games in class.}
        \resumeItem{Student}
          {Learned Tamil cultural values and literary works. Traditional classroom setting. Involved myself in interactive projects. Gave discourses on Tamil literary works and Tamil cultural events.}
      \resumeItemListEnd

    \resumeSubheading
      {Student Tutor}{Cupertino, CA}
      {AP Calculus BC}{Aug 2023 - present}
      \resumeItemListStart
        \resumeItem{Instruction}
          {Instructed class of 25+ students on basic concepts in calculus. Demonstrated thought processes, problem solving strategies and ensured student participation in lectures.}
        \resumeItem{Teaching Assistant}
          {Assisted teacher with planning lessons and instruction. Graded assignments and wrote test problems.}
        \resumeItem{Management}
            {Organized and maintained accurate record of test scores. Graded the homeworks' of 50+ students. Followed strict grading criteria. Wrote Free Response Questions using LaTeX. }
      \resumeItemListEnd
    \resumeSubheading
        {Monta Vista Game Development Club}{Cupertino, CA}
        {Co-founder and Vice-President}{Oct 2022 - present}
        \resumeItemListStart
            \resumeItem{VP}
                {Co-founded the club and presented the club to Monta Vista Student Association. Created outline of curriculum and taught Unity material to students. Introduced students to Unity API and C\#, Visual Studio and MonoBehavior API. Taught students how to draw basic 2-dimensional sprites. Taught basics of Unity Physics and Animation Engine and Prefabs. Taught students how to make basic game for their own game submissions to Ludum Dare.}
        \resumeItemListEnd
    \resumeSubheading
        {CADology}{Cupertino, CA}
        {Co-founder and Liaison}{June 2021 - July 2021}
        \resumeItemListStart
            \resumeItem{Co-founder}{Created outline for structure of classes, curriculum and goals. Gathered teachers. Ran successful outreach program to local community members, schools and social media platforms. Gathered 90+ students.}
            \resumeItem{Liaison}{Managed the development of curriculum. Created a safe working environment to ensure successful collaboration of teachers. Created meeting schedules and connected teachers to students to create a successful learning.}
        \resumeItemListEnd
    \resumeSubheading
        {Monta Vista Robotics Outreach Team}{Cupertino, CA}
        {FLL}{Oct 2021 - Dec 2021, Oct 2022 - Dec 2022}
        \resumeItemListStart
            \resumeItem{Tutor}{Assisted Robotics Liaisons with planning and coordination with members of local community. Aided students in creation of robots for FLL missions. Provided guidance on issues facing the world and potential solutions.}
        \resumeItemListEnd
    \resumeSubheading
        {Monta Vista Badminton Team}{Cupertino, CA}
        {Varsity Doubles}{Jan 2022 - Apr 2022, Jan 2023 - Apr 2023}
        \resumeItemListStart
            \resumeItem{Varsity Doubles}{Participated in weekly practices and games. }
        \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Scout App}
      {React Native application for gathering data during Robotics competitions integrated with back-end database.}
    \resumeSubItem{Super Scout Dashboard}
      {Data Visualization website made in React integrated with back end database for analyzing data to rank teams.}
    \resumeSubItem{Cascading Elevator}
      {Implemented physics concepts in code and used motion control techniques like Trapezoidal Motion, Motion Magic and tools like AdvantageScope to analyze and create smooth elevator motion.}
    \resumeSubItem{Climber}
        {Implemented PID motion control techniques, and worked with mechanical components like servos and ratchets to write code for a basic climber mechanism.}
    \resumeItem{Shef Scraper}
        {Combined postgreSQL's Javascript API with the shef API to scrape data from shef.com to gather information on customer orders.}
    \resumeItem{Autobing}
        {Used Javascript with the Puppeteer library to automate the process of obtaining bing reward points. Hosted to Firebase cloud functions to run daily.}
    \resumeItem{Audio Visualizer}
        {Used plain HTML, CSS and Javascript to create a custom audio visualizer.}
%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \resumeSubItem{Languages}{Javascript, Typescript, Python, Java, HTML, CSS, C\#, SQL, LaTeX, Spanish, Tamil}
    \resumeSubItem{Technologies}{WPILib, React, React Native, Firebase, Unity, postgreSQL, Visual Studio, VSCode}
     \resumeSubItem{Soft skills}{Leadership, Collaboration, Public Speaking, Critical Thinking, Mathematical Analysis}
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
